---
title       : Developing Data Products
subtitle    : Course Project (Slidify) Pitch Presentation
author      : ShuYi
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
output: 
  html_document: 
    keep_md: yes
---


## Overview
The prediction for miles per gallon(MPG) based on the horsepower, no. of cylinders and weight input by the user. 

The ShinyApp has been deployed. Click <a href="https://asy-devdataproduct.shinyapps.io/DevDataProduct">here</a> to launch the App.

--- .class #id 

## Dataset
mtcars dataset will be used for the miles per gallon (MPG) prediction
```{r}
data(mtcars)
head(mtcars, 5)
```

<h2>Source</h2>
Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391–411.

--- .class #id 

## Model
Linear model is used in this study to predict the fuel efficiency miles per gallon (MPG).
```{r}
Model <- lm(mpg ~ hp + cyl + wt, data=mtcars)

mpg <- function(hp, cyl, wt) {
  Model$coefficients[1] + Model$coefficients[2] * hp + 
    Model$coefficients[3] * cyl + Model$coefficients[4] * wt
}
```

--- .class #id 

## Graph plotting
```{r, echo=TRUE}
par(mfrow = c(2, 3))
plot(mtcars$hp, mtcars$mpg, main="MPG by Horsepower", xlab = "Horsepower"
     , ylab = "Miles Per Gallon (MPG)")
plot(mtcars$cyl, mtcars$mpg, main="MPG by Cylinders", xlab = "No. of Cylinder"
     , ylab = "Miles Per Gallon (MPG)")
plot(mtcars$wt, mtcars$mpg, main="MPG by Weight", xlab = "Weight"
     , ylab = "Miles Per Gallon (MPG)")
```


